A Survey of Real-Time Strategy Game AI\\ Research and Competition in StarCraft

### 2013-10-14 survey.tex
Updated bios

% \begin{IEEEbiographynophoto}{Santiago Onta\~{n}\'{o}n}
% is an assistant professor in the Computer Science Department at Drexel University. His main research interests are game AI, case-based reasoning and machine learning, fields in which he has published more than 90 peer-reviewed papers. He obtained his PhD form the Autonomous University of Barcelona (UAB), Spain. Before joining Drexel University, he held postdoctoral research positions at the Artificial Intelligence Research Institute (IIIA) in Barcelona, Spain, at the Georgia Institute of Technology (GeorgiaTech) in Atlanta, USA, and at the University of Barcelona, Spain.  
% \end{IEEEbiographynophoto}

% \begin{IEEEbiographynophoto}{Gabriel Synnaeve}
% is a post-doc in the Laboratory of Cognitive Science and Psycholinguistics
% (LSCP) at Ecole Normale Sup\'{e}rieure in Paris, France. Previously, he
% worked on Bayesian modeling in game AI research at INRIA (Grenoble) and
% Coll`{e}ge de France (Paris). He obtained his PhD in 2012 from Grenoble
% University, France.
% \end{IEEEbiographynophoto}

% \begin{IEEEbiographynophoto}{Alberto Uriarte}
% received the B.S. degree in Computer Science from Autonomous University of Barcelona (UAB), Spain, in 2006 and the M.S. degree in Computer Vision and Artificial Intelligence from Autonomous University of Barcelona (UAB), Spain, in 2011. He is currently pursuing the Ph.D. degree in computer science at Drexel University. His research interest includes game AI, RTS games, multiagents systems, procedural content generation, computational geometry, machine learning and drama management.  
% \end{IEEEbiographynophoto}

% \begin{IEEEbiographynophoto}{Florian Richoux}
%   is an associate  professor at the Laboratory of  Computer Science of
%   the University of Nantes,  France.  His main research field concerns
%   parallel  algorithms for solving  constraint-based problems  and has
%   strong  interests   in  AI,  in  particular  game   AI  and  machine
%   learning. He  obtained his Ph.D. in Theoretical  Computer Science at
%   the {\'E}cole Polytechnique  in 2009 and has been  for three years a
%   CNRS   research  fellow  at   the  Japanese-French   Laboratory  for
%   Informatics of the University of Tokyo, Japan.
% \end{IEEEbiographynophoto}

>>>>

\begin{IEEEbiographynophoto}{Santiago Onta\~{n}\'{o}n}
is an assistant professor in the Computer Science Department at Drexel University. His main research interests are game AI, case-based reasoning and machine learning, fields in which he has published more than 100 peer-reviewed papers. He obtained his PhD form the Autonomous University of Barcelona (UAB), Spain. Before joining Drexel University, he held postdoctoral research positions at the Artificial Intelligence Research Institute (IIIA) in Barcelona, Spain, at the Georgia Institute of Technology (GeorgiaTech) in Atlanta, USA, and at the University of Barcelona, Spain.  
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Gabriel Synnaeve}
is a post-doc in the Laboratory of Cognitive Science and Psycholinguistics
(LSCP) at Ecole Normale Sup\'{e}rieure in Paris, France. His current
research interests are deep learning and Bayesian nonparametrics to
model language acquisition from unsupervised speech and textual data.
Previously, he
worked on Bayesian modeling in game AI research at INRIA (Grenoble) and
Coll`{e}ge de France (Paris). He obtained his PhD in 2012 from Grenoble
University, France.
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Alberto Uriarte}
received the B.S. degree in Computer Science from Autonomous University of Barcelona (UAB), Spain, in 2006 and the M.S. degree in Computer Vision and Artificial Intelligence from Autonomous University of Barcelona (UAB), Spain, in 2011. He is currently pursuing the Ph.D. degree in computer science at Drexel University. His research interest includes game AI, RTS games, multiagents systems, procedural content generation, computational geometry, machine learning and drama management.  
 \end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Florian Richoux}
   is an associate  professor at the Laboratory of  Computer Science of
   the University of Nantes,  France.  His main research field concerns
   parallel  algorithms for solving  constraint-based problems  and has
   strong  interests   in  AI,  in  particular  game   AI  and  machine
   learning. He  obtained his Ph.D. in Theoretical  Computer Science at
   the {\'E}cole Polytechnique  in 2009 and has been  for three years a
   CNRS   research  fellow  at   the  Japanese-French   Laboratory  for
   Informatics of the University of Tokyo, Japan.
 \end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{David Churchill}
is a PhD student in the Computing Science department at the University of Alberta, Canada. He obtained his MSc in Computer Science in the field of autonomous robotics from Memorial University of Newfoundland, Canada. His main research interests are in real-time strategy video game AI, specifically in real-time heuristic search techniques for StarCraft. Since 2011 he has been the co-organizer and facilitator of the AIIDE StarCraft AI Competition, as well as author of UAlbertaBot. 
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Mike Preuss}
is a research associate at the European Research Center for Information Systems (ERCIS), Muenster University, Germany. He received his Diploma degree in 1998 from TU Dortmund, Germany. He is interested in multimodal and multiobjective niching for evolutionary algorithms on real-valued problems, and in applying this methods to various engineering domains and computer games. In the Computational Intelligence in Games (CIG) area, he is especially active in real-time strategy games (RTS) and procedural content generation (PCG). He was involved in founding the EvoGames track at Evo* and the Digital Entertainment Technologies and Arts (DETA) track at GECCO and organized the StarCraft competitions at CIG from 2011 to 2013.
\end{IEEEbiographynophoto}
